On the Functionality of the Multilayer Perceptron

### 2020-12-03 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Properties of musical instruments

\begin{titlepage}
	\begin{center}
   		\vspace*{1cm}
       	\begin{LARGE}
       	\textbf{Classifying Chaotic Synthesizers with a Multimodal Neural Network} \\
       	\end{LARGE}
       	\vspace{1cm}
       	\begin{Large}
       	\textcolor{red}{Thesis Subtitle}
       	\end{Large}             
       	\vspace{1.5cm}

@@

\paragraph*{}The ability to classify time-series data into unique categories has become topic of much attention in the last few decades \cite{Khan}. These signals can take the form of day-to-day topics such as weather measurements, financial reports, or audio-visual media, and extend into more niche disciplines of medicine, physics, and digital signal processing.

\paragraph*{}Recent progress in high performance computing and computational efficiency have given rise to another burst

@@

\paragraph*{}We have assembled training data samples than can be grouping in 38 classes of unique sources listed below:

@@

\paragraph*{}We can model a chordophone as having a string of length $L$, with a constant linear mass density, $\mu$, subject to a tension force $F_T$. The string is flexible, and free to vibrate in a single dimension. We describe the state of string over space and time with a function $U(x,t)$. The behavior of the string can be modeled by D'Alembert's 1-dimensional wave equation \cite{Haberman,Taylor}:
\begin{equation}
\label{eqn-1DWaveEqn}
\frac{\partial^2 U}{\partial t^2} = v^2 \frac{\partial^2 U}{\partial x^2}
\end{equation}
Where $v$ is the wave propagation velocity, given by $\sqrt{\frac{F_T}{\mu}}$. Additionally, the string is fixed in place at both ends, with a nut at $x = 0$ and a bridge at $x = L$, which can be modeled by the boundary conditions \cite{Olson,White,Haberman}:
\begin{equation}
U(0,t) = 0 
	\text{\hspace*{2cm} and \hspace*{2cm}}
U(L,t) = 0 
\end{equation}

\paragraph*{}In order to specify a solution, we must also specify two initial conditions. We described the initial state of the string at time $t = 0$  by the two conditions:
\begin{equation}
U(x,0) = f(x) 
	\text{\hspace*{2cm} and \hspace*{2cm}}
\frac{\partial U}{\partial t}(x,0) = g(x)
\end{equation}
Depending on the exact nature of the source instrument, $f(x)$ and $g(x)$ can take on different forms. For example, for plucked stringed instruments, $f(x)$ may appear to be as triangle-like function, with a peak at some position $0 < x_0 < L$ where then string was struck. $g(x)$

\paragraph*{}We explore solutions that take the form \cite{Haberman}:
\begin{equation}
U(x,t) = \psi(x)h(t)
\end{equation}
From this separation, we find that $\psi(x)$ and $h(t)$ each are composed of a linear combination of orthogonal trigonometric functions. Applying the boundary and initial conditions to the system allows for a linear combination of solutions \cite{Haberman}:
\begin{equation}
U(x,t) = 
\sum_{n=1}^{\infty} \bigg( A_n \sin\big(\frac{n\pi x}{L}\big)\cos\big(\frac{n\pi vt}{L}\big)
+ B_n \sin\big(\frac{n\pi x}{L}\big)\sin\big(\frac{n\pi vt}{L}\big) \bigg)
\end{equation}
The initial conditions are satisfied if:
\begin{equation}
\begin{array}{ll}
    f(x) = \sum_{n=1}^{\infty} A_n \sin\big(\frac{n\pi x}{L}\big) \\
    g(x) = \sum_{n=1}^{\infty} B_n\big(\frac{n\pi v}{L}\big)
    			\sin\big(\frac{n\pi x}{L}\big)
\end{array} 
\end{equation}
Where $A_n$ and $B_n$ are given by:
\begin{equation}
\begin{array}{ll}
    A_n = \frac{2}{L} \int_{0}^{L} f(x) \sin\big(\frac{n\pi x}{L}\big) dx \\
    B_n = \frac{2}{n\pi v} \int_{0}^{L} g(x) \sin\big(\frac{n\pi x}{L}\big) dx \\
\end{array} 
\end{equation}

\subsubsection{Consequences of the Wave Equation}

\paragraph*{}The solution that we have derived from the wave equation shows that the behavior of $U(x,t)$ is greatly dependent on the nature of the string's initial shape, $f(x)$, when struck. In the case of picked or plucked instruments, the initial shape of $f(x)$ would be something like a "ramp function":
\begin{equation}
\label{eqn-RampFunc}
f(x) =
\end{equation}

@@

>>>>

\begin{titlepage}
	\begin{center}
   		\vspace*{1cm}
       	\begin{LARGE}
       	\textbf{Mapping Chaotically Generated Synthesizers to Real World Instruments with Machine Learning and Harmonic Analysis} \\
       	\end{LARGE}
       	\vspace{1cm}
       	\begin{Large}
       	\textcolor{red}{Thesis Subtitle}
       	\end{Large}             
       	\vspace{1.5cm}

@@

\paragraph*{}The ability to classify time-series data into unique categories has become topic of much attention in the last few decades \cite{Khan}.Whether its climate measurements, financial reports, audio-visual media, or medicine complex signal surround the modern world at every corner.

\paragraph*{}Recent progress in high performance computing and computational efficiency have given rise to another burst in the

@@

\paragraph*{}We have assembled training data samples than can be grouping into $37$ classes of unique sources listed below:

@@

\paragraph*{}We can model a chordophone as having a string of length $L$, with a constant linear mass density, $\mu$, subject to a tension force $F_T$. The string is flexible, and free to vibrate in a single dimension. We describe the state of string over space and time with a function $U(x,t)$. The behavior of the string can be modeled by D'Alembert's 1-dimensional wave equation \cite{Haberman,Hunter,Taylor}:
\begin{equation}
\label{eqn-1DWaveEqn}
\frac{\partial^2 U}{\partial t^2} = v^2 \frac{\partial^2 U}{\partial x^2}
\end{equation}
Where $v$ is the wave propagation velocity, given by $\sqrt{\frac{F_T}{\mu}}$. D'Alembert's equation indicates that the acceleration of any point on a string is directly proportional to the rate of change of the slope of the string at that point. Additionally, the string is fixed in place at both ends, with a nut at $x = 0$ and a bridge at $x = L$, which can be modeled by the boundary conditions \cite{Olson,White,Haberman}:
\begin{equation}
U(0,t) = 0 
	\text{\hspace*{2cm} and \hspace*{2cm}}
U(L,t) = 0 
\end{equation}

\paragraph*{}In order to specify a solution, we must also specify two initial conditions. We described the initial state of the string at time $t = 0$  by the two conditions:
\begin{equation}
U(x,0) = f(x) 
	\text{\hspace*{2cm} and \hspace*{2cm}}
\frac{\partial U}{\partial t}(x,0) = g(x)
\end{equation}
Depending on the exact nature of the source instrument, $f(x)$ and $g(x)$ can take on different forms. For example, for plucked stringed instruments, $f(x)$ may appear to be as triangle-like function, with a peak at some position $0 < x_0 < L$ where then string was struck. It is these initial conditions that allow for the drastically different timbres that arise in the wave forms.

\paragraph*{}Despite these differences, the wave equation is a \textit{linear} partial differential equation which allows for the fact that a linear combination of solutions is also a valid solution. In the case of the taught finite string that is fixed at both ends, such a guitar, viola or cello, the a solution tends to take the form of a sinusoidal function such a sine or cosine \cite{Hunter, Taylor, White}.

\paragraph*{}The boundary continuations, and most forms of standard initial conditions allow for the each sinusoidal to fit exactly an integer wavelengths into the region $[0,L]$ \cite{Haberman,Hunter}. Physically, this corresponds to having the string vibrate with some fundamental frequency $f_0$, which represents it's lowest possible note,and a linear combination of higher harmonics, $n \times f_0$, where $n \in \mathbb{Z}$ \cite{Olson,Taylor,White}.

\begin{figure}[H]
	\begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[scale=0.18]{../FiguresSpectrogram/CELLO-F4}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[scale=0.18]{../FiguresSpectrogram/Guitar-B2}
	\end{subfigure}
\end{figure}

@@

\bibitem{Hunter}
Hunter, Joseph L. \textit{Acoutics}. Prentice Hall, 1957.
